% License : MIT
%------------------------

\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{comment}
% fix for pandoc 1.14
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% \usepackage[sfdefault]{FiraSans} %% option 'sfdefault' activates Fira Sans as the default text font
% \usepackage[T1]{fontenc}
% \renewcommand*\oldstylenums[1]{{\firaoldstyle #1}}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{}{\Large Joaquim Ignatious Monteiro}} & Email : \href{mailto:joaquim@cet.ac.in}{joaquim@cet.ac.in}\\
  \href{https://jim79.github.io}{https://jim79.github.io} & Mobile : 9447818985 \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    % \resumeSubheading
      % {APJ Abdul Kalam Technological University}{India}
      % {PhD}{Pursuing}
    \resumeSubheading
      {Indian Institute of Technology Bombay}{India}
      {Master of Technology in Biomedical Engineering.}{2010}
    \resumeSubheading
      {Mahatma Gandhi University Kottayam}{India}
      {Bachelor of Technology in Electronics and Communication Engineering}{2001}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
    {Department of Technical Education}{Kerala, India}
    {Assistant Professor}{2005 June - Present}

    \resumeSubheading
    {Viswajyothi College of Engineering and Technology}{Kerala, India}
    {Lecturer}{2003 May - 2005 May}

    \resumeSubheading
      {Model Engineering College}{Kerala, India}
      {Adhoc Lecturer}{2002 - 2003}
      
  \resumeSubHeadingListEnd
  
  \resumeSubHeadingListStart
   \resumeSubItem{Current Institution}
     {Department of Electronics \& Communication Engineering, \\ \hspace*{105pt}College of Engineering Trivandrum}
     \resumeSubHeadingListEnd
 \section{Publications}
     \resumeSubHeadingListStart
       \resumeSubItem{SCOPUS ID}
       {55839822200}
       
       \resumeSubItem{ORCID iD}
       {https://orcid.org/0000-0002-5935-2794} 
       
     \resumeSubHeadingListEnd
     
\begin{comment}   
\section{Select Publications}
\begin{itemize}
\tightlist
\item
A. Tharakan and J. I. Monteiro, “Design and analysis of piezoelectric microcantilever energy harvesters,” Proceedings of the 2019 9th International Conference on Advances in Computing and Communication, ICACC 2019, pp. 73–78, 2019.
\item
L. J. Mohan and J. Ignatious, “Navigation of Mobile Robot in a Warehouse Environment,” Jul. 2018. doi: 10.1109/icetietr.2018.8529012.
\item 
U. S. Nath, C. R. Arunima, R. Jaisha, U. P. Amjad, and J. I. Monteiro, “A Standalone Open Hardware System for ECG Detection and Classification,” 2018 9th International Conference on Computing, Communication and Networking Technologies, ICCCNT 2018, 2018.
\item 
J. I. Monteiro, S. Mukherji, and T. Kundu, “Development of a low-cost portable surface plasmon resonance biosensor,” 2013 Annual International Conference on Emerging Research Areas, AICERA 2013 and 2013 International Conference on Microelectronics, Communications and Renewable Energy, ICMiCR 2013 - Proceedings, 2013.
\item 
G. E. John and J. I. Monteiro, “WSN technologies for low data rate and power constrained applications,” 2014 1st International Conference on Computational Systems and Communications, ICCSC 2014, pp. 116–121, 2003.
\end{itemize}
\end{comment}

% --------RESEARCH INTERESTS------------
\section{Areas of Interest}
    Embedded Systems \& IoT, Signal Processing

% --------PROGRAMMING SKILLS------------
\section{Skills and Tools}
 \resumeSubHeadingListStart
   \resumeSubItem{Programming Languages}
     {Python, C, Matlab}
   \resumeSubItem{Machine Learning Frameworks}
     {PyTorch, Scikit-Learn, pandas}
     \resumeSubHeadingListEnd
     
% --------Language SKILLS------------
\section{Languages}
\resumeSubHeadingListStart
  \item{
    \textbf{Malayalam}{: native}
    \textbf{English}{: fluent }
    \textbf{Hindi}{: fluent }
  }
\resumeSubHeadingListEnd
     
\end{document}
